Structural Breaks in Inflation Dynamics within the European Monetary Union

### 2010-10-13 pkg/paper/Draft/draft-Z-W.tex
finished slides and table for countries slides.Rnw should be executed within the Analysis Results environment since it needs datasets
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/glogis@49 b679b2f7-6539-45d0-a605-5ddcb976cde9

\multirow{4}{*}{Belgium} & 1991(2)--1999(12)   & 2001(1)--2010(3) & -- & 1979(1) & 1999(1) \\ 

@@

\multirow{4}{*}{Slovakia} & 1995(2)--1997()   & 1997(5)--2004(2) & 2004(3)--2010(3) & 2005(11) & 2009(1) \\ 

@@

On the basis of the results, we can trace out 6 groups of countries with rather distinct behavior. Group 1 consists of Italy and Spain (both very similar) and possibly Belgium, Luxembourg and Portugal. Group 2 is an Eastern European group comprising Poland, the Czech Republic, Slovenia, Slovakia and Hungary. Group 3 is a Non-ERM~II member group including Sweden and the United Kingdom. The Netherlands, Greece and Finland build group 4 which exhibits no changes. Group 5 is composed of France, Germany, Austria and Denmark. Ireland stands on its own and is the only country which changed its inflation dynamics as an after march of the financial crises of 2008. \\
What we can observe for almost all the EURO countries is an increase in variance and mean, with the exception of Ireland. Since inflation volatility increased in all countries, we find no proof of a common claim that inflation uncertainty may increase in countries that have a smaller influence on ECB policy. \\
Lets consider a few countries in broader detail to get an idea about what happened. In Austria we see evidence of a change in the inflation rate, when the old regime ended in September 2007. The new regime is much more volatile, with an almost threefold increase in variance.

>>>>

\multirow{4}{*}{Belgium} & 1991(2)--1999(12)   & 2000(1)--2010(3) & -- & 1979(1) & 1999(1) \\ 

@@

\multirow{4}{*}{Slovakia} & 1995(2)--1997(4)   & 1997(5)--2004(2) & 2004(3)--2010(3) & 2005(11) & 2009(1) \\ 

@@

On the basis of the results, we can trace out 6 groups of countries with rather distinct behavior. Group 1 consists of Italy and Spain (both very similar) and possibly Belgium, Luxembourg and Portugal. Group 2 is an Eastern European group comprising Poland, the Czech Republic, Slovenia, Slovakia, Estonia and Hungary. Group 3 is a Non-ERM~II member group including Denmark, Sweden and the United Kingdom. The Netherlands, Greece and Finland build group 4 which exhibits no changes. Group 5 is composed of France, Germany, and Austria. Ireland stands on its own and is the only country which changed its inflation dynamics as an after march of the financial crises of 2008. \\
What we can observe for almost all the EURO countries is an increase in variance and mean, with the exception of Ireland. Since inflation volatility increased in all countries, we find no proof of a common claim that inflation uncertainty may increase in countries that have a smaller influence on ECB policy. \\
Lets consider a few countries in broader detail to get an idea about what happened. In Austria we see evidence of a change in the inflation rate, when the old regime ended in September 2007. The new regime is much more volatile, with an almost threefold increase in variance.
